\documentclass{article}
\usepackage[a4paper]{geometry}
\usepackage{geometry}
\geometry{a4paper, portrait, margin=0.5in}
\usepackage{hyperref}
\hypersetup{
    colorlinks=true,
    urlcolor=blue,
}

\title{Albert Kapitanov}
\author{Software Development Engineer/Software Architect}
\date{}

\begin{document}
\maketitle

A backend developer with a focus on software design and architecture having 10+ years of experience.
Engaged in the development and support of web and desktop applications, both developing new features and
migrating from legacy stack to modern technologies and tools.
Main responsibilities were design and development of server parts of
web applications, development of desktop applications for Windows, database and infrastructure
design.

Primary programming language and platform are C\#/.NET (Core). Also has notable experience with Golang and JavaScript ecosystem including frontend development and development of utilitary web services on NodeJS platform.

\section*{Contracts}

\begin{itemize}
  \item Email: \href{mailto:albert.kapitanov.77@gmail.com}{albert.kapitanov.77@gmail.com}
  \item LinkedIn: \href{https://www.linkedin.com/in/albertkapitanov}{linkedin.com/in/albertkapitanov}
  \item GitHub: \href{https://github.com/kapitanov}{github.com/kapitanov}
  \item Leetcode: \href{https://leetcode.com/albert-k}{leetcode.com/albert-k}
  \item Telegram: \href{https://t.me/albert_kapitanov}{@albert\_kapitanov}
  \item Phone: \href{tel:+79032754861}{+7 903 275 48 61}
\end{itemize}

\section*{Education}

\begin{itemize}
    \item {
        Master of Engineering and Technology (2011) at National Research University of
Electronic Technology, Moscow (MIET)
    }
    \item {
        Bachelor of Engineering and Technology (2009) at National Research University of
Electronic Technology, Moscow (MIET)
    }
    \item {
        Microsoft Certified Professional (since 2012, MCID: 8528114)
    }
\end{itemize}

\section*{Technical skills}

\begin{itemize}
    \item {
        Backend: C\#, .NET Framework, .NET Core, Golang, NodeJS, ASP.NET Core, Entity Framework, xUnit, Moq, Dapper, Newtonsoft.JSON, WPF, SOAP.
    }
    \item {
        Frontend: JavaScript, Typescript, VueJS, Blazor Server, React, Angular, HTML, CSS.
    }
    \item {
        Software architecture: Domain Driven Design, Test Driven Design, RESTful API, Design Patterns, SOLID, OOP, OpenAPI.
    }
    \item {
        Databases and message queues: PostreSQL, MS SQL Server, MongoDB, Redis, Memcached, Kafka, RabbitMQ.
    }
    \item {
        Infrastructure: Docker, Docker Compose, Kubernetes, Bitbucket Pipelines, Gitlab Pipelines.
    }
    \item {
        IDEs and tools: Visual Studio, VSCode, Rider, DataGrip, GoLand, Bash, Powershell.
    }
    \item {
        Version control: Git, Subversion
    }
\end{itemize}

\section*{Professional experience}

\begin{itemize}
    \item {
        \textbf{Remote medical services system}
        
        Project case: a system to provide remote medical services, including text chats and remote video calls with a doctor.
        
        Role(s) on project: Lead Backend Developer, Tech Lead.
        
        Achievements:
        
            \begin{itemize}
                \item Co-designed overall system architecture.
                \item Rapidly prototyped a video call proof-of-concept application.
                \item Created few microservices, including user management subsystem, single sign-on service and video call subsystem.
            \end{itemize}
        
        Technologies: Golang, WebRTC, PostgreSQL, Redis, Kafka, WebSocket, REST API, JWT.
    }
    \item {
        \textbf{Online trading game demo}
        
        Project case: a prototype for an online education game focused on security market trading.
        
        Role(s) on project: Lead Backend Developer.
        
        Achievements:
        
            \begin{itemize}
                \item Created server side logic for a game loop.
                \item Implemented a game bot for a single player mode.
            \end{itemize}
        
        Technologies: Golang, Redis, REST API.
    }
    \item {
        \textbf{Web system for bond trading and analysis.}
        
        Project case: a website and a mobile app for complicated bond information search, analysis and trading.
        
        Role(s) on project: Software Architect, Lead Backend Developer.
        
        Achievements:
        
            \begin{itemize}
                \item Designed a microservice-based high-performance system to serve both static and real-time bond data.
                \item Designed and implemented a bond porfolio recommender subsystem.
                \item Implemented an incremental ETL data loader with incremental data recalculation "in-database".
            \end{itemize}
        
        Technologies: C\#, .NET 5, React, Typescript, REST API, PostgreSQL, Redis, RabbitMQ, OpenAPI.
    }
    \item {
        \textbf{Option hedge fund trading system.}
        
        Project case: A realtime option marketdata monitoring system and a trading bot with a custom trading strategy.
        
        Role(s) on project: Backend Developer, Frontend Developer.
        
        Achievements:
        
            \begin{itemize}
                \item  Created a custom secure communication layer featuring real-time bidirectional messaging, two-way SSL pinning and an SBE-based compact binary serialization.
                \item Put extra focus on keeping communication layer allocation-effective, reaching nearly zero allocation count on a hot path.
                \item Implemented real-time frontend components using Blazor Server technology.
            \end{itemize}
        
        Technologies: C\#, .NET 5, ASP.NET Core, Blazor Server, SBE binary encoding, Twime binary protocol.
    }
    \item {
        \textbf{Cryptocurrency exchange system.}
        
        Project case: A backend system and a web terminal for a cryptocurrency exchange.
        
        Role(s) on project: Software Architect, Lead Backend Developer.
        
        Achievements:
        
            \begin{itemize}
                \item Designed and implemented low-level real-time communication layer, featuring RPC, Pub/Sub, data streaming, failure recovery, low latency, high throughput and zero allocations on a hot path.
                \item Designed and implemented a high-performance order matching engine supporting various order types and match strategies.
                \item Created a set of integration modules for external services including cryptocurrency wallet services.
                \item Designed a data-driven streaming real-time architecture for order processing, marketdata generation and financial clearing.
                \item  Created a high-performance WebSocket API gateway with extendable JSON-based protocol.
            \end{itemize}
        
        Technologies: C\#, .NET Core, React, Typescript, WebSocket, MongoDB, PostgreSQL, Docker.
    }
    \item {
        \textbf{Electronic document exchange system}
        
        Project case: A system designed to provide a way of financial document exchange between corporations and bank.
        
        Role(s) on project: Backend Developer, Frontend Developer
        
        Achievements:
        
            \begin{itemize}
                \item Created an initial project structure.
                \item Implemented core user interface components.
            \end{itemize}
        
        Technologies: C\#, .NET Core, ASP.NET Core, PostgreSQL, Angular, Typescript.
    }
    \item {
        \textbf{Security trade marketplace}
        
        Project case: a website that allows clients to perform trades on securities via different brokers,
        providing a unified broker-independent way to trade securities.
        
        Role(s) on project: Lead Backend Developer.
        
        Achievements:
        
            \begin{itemize}
                \item Created a parser/formatter for STOMP protocol.
                \item Implemented a microservice-based system with communication over RabbitMQ (RPC style).
            \end{itemize}
        
        Technologies: C\#, .NET Core, ASP.NET Core, WebSocket, STOMP, PostgreSQL, RabbitMQ.
    }
    \item {
        \textbf{Over-the-counter trade system}
        
        Project case: a web terminal to find a counterparty for an over-the-counter trade,
        a back office for trade lifecycle.
        
        Role(s) on project: Software Architect, Backend Developer.
        
        Achievements:
        
            \begin{itemize}
                \item Designed an extendable electronic document workflow engine.
                \item Implemented a digital signature verification module based on CryptoPRO crypto provider.
                \item Created a real-time API for document state updates.
                \item Created a statistic data generator for marketdata reports.
            \end{itemize}
        
        Technologies: C\#, .NET Framework, ASP.NET MVC, MS SQL Server, IIS, AngularJS, Typescript, SignalR, CryptoPRO crypto provider.
    }
    \item {
        \textbf{Desktop product management system}
        
        Project case: a web service that provides licensing, update package delivery, license purchasing and telemetry collection for various desktop products.
        
        Role(s) on project: Software Architect, Lead Backend Developer.
        
        Achievements:
        
            \begin{itemize}
                \item Designed a monolithic web application with horizontal scalability capability.
                \item Designed a product-agnostic software licensing mechanism based on asymmetric signature with both online and offline licensing session support.
                \item Migrated backend services from docker-compose-based deployment to a Kubernetes cluster.
                \item Created components for internal user interface using Blazor Server framework.
            \end{itemize}
        
        Technologies: C\#, .NET 5, ASP.NET Core, MongoDB, RabbitMQ, Blazor Server, WebSocket, Docker/Docker-Compose, Kubernetes.
    }
    \item {
        \textbf{Security structure information service}
        
        Project case: a web service that provides information on tradable securities on various exchanges, including assets and derivatives.
        
        Role(s) on project: Software Architect, Lead Backend Developer.
        
        Achievements:
        
            \begin{itemize}
                \item Designed a high-performance web service providing security information.
                \item Created a failure-proof ETL process to collect security information from various sources and transform it into a unified representation. 
                \item Created a multi-datacenter data replication system working over S3 object storage.
                \item Implemented a database-level transactions for MongoDB.
                \item Migrated an earlier version of the project from .NET Framework to .NET 5.
                \item Created an effective caching mechanism working over NGINX on HTTP level.
            \end{itemize}
        
        Technologies: C\#, .NET Framework/.NET 5, ASP.NET MVC/ASP.NET Core, MongoDB,  Docker/Docker-Compose, Kubernetes, NGINX.
    }
    \item {
        \textbf{Cryptography service}
        
        Project case: a Windows application that allows JavaScript client code to sign an arbitrary string of data using Validata crypto provider.
        
        Role(s) on project: Backend Developer.
        
        Achievements:
        
            \begin{itemize}
                \item Created components of user interface.
                \item Created an MSI installer package.
            \end{itemize}
        
        Technologies: C\#, NET Framework, WPF, Validata crypto provider.
    }
    \item {
        \textbf{Central trade reporting repository}
        
        Project case: a central repository for financial trade reporting from various legal entities.
        
        Role(s) on project: Backend Developer.
        
        Achievements:
        
            \begin{itemize}
                \item Created a REST API for data requests.
                \item Created new methods for SOAP web service.
            \end{itemize}
        
        Technologies: Java, Oracle WebLogic, Oracle Database, SOAP.
    }
    \item {
        \textbf{Cryptography Java Applet}
        
        Project case: a Java applet (a browser application) that allows JavaScript client code to sign an arbitrary string of data using Validata crypto provider.
        
        Role(s) on project: Developer.
        
        Achievements:
        
            \begin{itemize}
                \item Created a Java applet with ability to interact with JavaScript code.
                \item Designed a JavaScript API that supports transferring of base64-encoded data streams of an unlimited length from JS to Java applet and back.
            \end{itemize}
        
        Technologies: Java, Validata crypto provider.
    }
    \item {
        \textbf{Central trade reporting repository web interface}
        
        Project case: a web interface for central trade repository that allows clients to view, modify and upload data.
        
        Role(s) on project: Lead Backend Developer
        
        Achievements:
        
            \begin{itemize}
                \item Created a customized authorization subsystem. 
                \item Created a mechanism to securely decrypt encrypted data packages without exposing client decryption keys to the server side.
                \item Created a OAuth2.0-compatible single sign-on endpoint.
            \end{itemize}
        
        Technologies: C\#, .NET Framework, ASP.NET MVC, MS SQL Server, Validata crypto provider, SOAP web services.
    }
    \item {
        \textbf{Integration gateway for trade reporting repository}
        
        Project case: a Windows application that sends and receives electronic documents to and from central trade reporting repository.
        
        Role(s) on project: Developer.
        
        Achievements:
        
            \begin{itemize}
                \item Created robust electronic document analysis engine.
                \item Implemented a customized SOAP client supporting a non-standard TLS encryption algorithm provided by an external crypto provider.
                \item Designed and implemented a directory monitoring component that supports file dependencies and is prone to i/o errors.
            \end{itemize}
        
        Technologies: C\#, .NET Framework, WPF, Validata crypto provider, SOAP web services, SQLite.
    }
    \item {
        \textbf{Option trading and analysis terminal}
        
        Project case: a Windows desktop application that provides various tools on option analysis, trading and trade automation.
        
        Role(s) on project: Lead Developer, Software Architect.
        
        Achievements:
        
            \begin{itemize}
                \item Designed an internal application data model.
                \item Created a component based application framework supporting plug-ins with licensing-driven activation.
                \item Implemented a set of extendable user interface components.
                \item Created few integration modules for different broker systems.
            \end{itemize}
        
        Technologies: C\#, .NET Framework/.NET 6, WPF, SQLite.
    }
    \item {
        \textbf{Financial-related education platform}
        
        Project case: a platform for education video courses primarily focused on financial-related education courses.
        
        Role(s) on project: Backend Developer
        
        Achievements:
        
            \begin{itemize}
                \item Designed a flexible rule-based authorization component.
            \end{itemize}
        
        Technologies: C\#, .NET Framework, MS SQL Server, ASP.NET, GraphQL.
    }
    \item {
        \textbf{Self-hosted back office system for over-the-counter trades}
        
        Project case: a self-hosted system that collects over-the-counter trades and provides a set of tools to manage them.
        
        Role(s) on project: Software Architect, Lead Backend Developer.
        
        Achievements:
        
            \begin{itemize}
                \item Designed a microservice based solution that uses HTTP protocol to wire microservices together.
                \item Created a host program to deploy microservices as a whole on premises.
                \item Implemented few microservices for the system.
            \end{itemize}
        
        Technologies: Golang, C\#, .NET Core, PostgreSQL.
    }
    \item {
        \textbf{Desktop Market Maker Software}
        
        Project case: a Windows application that works as a Market Maker trading bot on futures market.
        
        Role(s) on project: Developer.
        
        Achievements:
        
            \begin{itemize}
                \item Created a project's framework code.
                \item Added integrations with various external trade interfaces.
                \item Created few user interface components and pages.
            \end{itemize}
        
        Technologies: C\#, .NET Framework, WPF.
    }
\end{itemize}

\end{document}
